\textsf{Are large language models superhuman chemists?}

### 2024-04-01 src/tex/appendix.tex
[showyourwork]
feat: add requires-calc analysis

>>>>

In addition, we analyzed the performance on questions which requires calculation. For this, we manually labeled questions that require multiple calculation steps. 
We find that the ranking of models is different for questions with our without calculations (\Cref{fig:requires_cal}).

\begin{figure}
    \centering
    \includegraphics{figures/model_overall_cal.pdf}
    \caption{\textbf{Overall model performance for questions with and without calculation steps.} We find that the ranking of models changes if we evaluate them on questions that require and do not require calculations, respectively.}
    \script{requires_calculation_plot.py}
    \label{fig:requires_cal}
\end{figure}
